A Grimm idea

### 2016-05-03 presentation/main.tex
presentation right before simulation

\usepackage[utf8]{inputenc}
\usepackage{epigraph}
\usepackage{tikz}

@@

\begin{frame}
  \frametitle{}
\end{frame}
\end{document}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{epigraph}
\usepackage{tikz}
\usepackage{todonotes}

@@

\begin{frame}
  \frametitle{Closed walk}
  \begin{theorem}
    A exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ produces a closed walk.
  \end{theorem}
  \begin{itemize}
    \item Introduce triple $(v,l,i)$ with vertex $v$ is entered
      through port $l$ and $e_{i}$ is the next turn
    \item Note that there is exactly one $(v,l,i) \leadsto (v',l',i')$
    \item Furthermore assume $t_{1} = (v',l',i') \leadsto (v,l,i)$ and
      $t_{2} = (v'',l'',i'') \leadsto (v,l,i)$:
      \begin{itemize}
        \item $t_{1}$ and $t_{2}$ both entered $v$ through $l$: $v' = v''$
        \item $t_{1}$ and $t_{2}$ lead that $i$ is the next turn: $i' = i''$
        \item $l' + e_{i'} \mod d_{v'} = l'' + e_{i''} \mod d_{v''}$ and
          $l',l''\leq d_{v'} = d_{v''}$: $l' = l''$
      \end{itemize}
    \item Only finite triples, thus projection to vertices yields closed walk
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Exploring pebble machine}
  \alt<+>{
    \begin{theorem}[Reingold]
      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement producing
      a universal exploration sequence for every regular graph with $n$ vertices.
    \end{theorem}
  }{
    \begin{theorem}
      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n)$ that moves
      along a closed walk with $n$ distinct vertices (or explores the whole
      graph).
    \end{theorem}
  }
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
      \item<3-> Establish 3-regularity
        \begin{itemize}
          \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
          \item TODO: ADD BOUNDARY
        \end{itemize}
      \item<5-> Use $A$ and take first $k = 3n\cdot c$ ($c$ number of
        configurations $M_{A}$)
    \end{itemize}
    \column{0.5\textwidth}
    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Tape simulation via pebbles}
\end{frame}
\end{document}
